---
output:
  html_document: default
---
<!DOCTYPE html>
<html>
  <head>
    <title>DSCI 521 Lab 4 Question 10</title>
    <meta charset="utf-8">
    <style>
      @import url(https://fonts.googleapis.com/css?family=Yanone+Kaffeesatz);
      @import url(https://fonts.googleapis.com/css?family=Droid+Serif:400,700,400italic);
      @import url(https://fonts.googleapis.com/css?family=Ubuntu+Mono:400,700,400italic);

      body { font-family: 'Droid Serif'; }
      h1, h2, h3 {
        font-family: 'Yanone Kaffeesatz';
        font-weight: normal;
      }
      .remark-code, .remark-inline-code { font-family: 'Ubuntu Mono'; }
    </style>
  </head>
  <body>
    <textarea id="source">

class: center, middle





Courses in Block One

---

# DSCI 521

Computing Platforms for Data Science
- Instructor: Florencia D’Andrea

---

# DSCI 551

Descriptive Statistics and Probability for Data Science
- Instructor: Alexi Rodríguez-Arelis
- We have found expected values:
- example: Rolling a die!
```{r}
((1/6 * 1) + (1/6 * 2) + (1/6 * 3) + (1/6 * 4) + (1/6 * 5) + (1/6 *6))
```
---

# DSCI 523

Programming for Data Manipulation
- Instructor: Gittu George
- We use R for programming in this course, 
- example:
```{r}
print(3+4)
```

---

# DSCI 511

Python Programming for Data Science
- Instructor: Arman Seyed-Ahmadi

    </textarea>
    <script src="https://remarkjs.com/downloads/remark-latest.min.js">
    </script>
    <script>
      var slideshow = remark.create();
    </script>
  </body>
</html>